---
title: "Lab 6"
author: "Evie Vermeer"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

### Example of a rank-based test

We'll make our own samples, using a pseudorandom generator

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424) 
gp_2 <- sample.int(30, size = 15, replace = TRUE)

```

```{r}
hist(gp_1)
hist(gp_2)
```

Try a t-test
```{r}
t.test(gp_1,gp_2)
```

This P-value means that if these samples come from populations with the same mean, then there is a 19.8% chance that other samples will have means that are this or more different. 
"If these samples were drawn from populations with the same mena, the propbability of taking two random samples with means *at least as different* as the sample means we found by random chance (taking into account spread, n) is 19.8%. 
Retain (fail to reject) the null hypothesis >> There is no significant difference in means between group 1 and group 2. 

DON'T say accept null hypothesis. 

Now let's compare this t-test outcome to a rank-based test. 

### Mann Whitney U unpaired rank-based test
```{r}
mwu <- wilcox.test(gp_1,gp_2)

mwu
```
The P-value of .28 means that if these samples come from populations with the same ranks of values (or medians), then there is a 28% chance that other samples will have ranks of values (or medians) that are at least this different. 

Retain the null hypothesis >> There is no significant difference in ranks (often you'll see medians) between group 1 and group 2. 

Median scores for group 1 (M=14) and group 2(M=12) did not differ significantly (Mann-Whitney U test: U(df) = 86, p =.28)

### Linear Regression

Simple linear regression (single dependent variable, a single independent variable)

```{r,} 
# Make an exploratory plot of penguin body mass (y-axis) versus flipper length (x-axis). include = FALSE to leave out of final doc 
ggplot(data=penguins, aes(x= flipper_length_mm, y = body_mass_g)) + 
geom_point() + 
  geom_smooth(method = "lm")

```

Find a linear regression model using ordinary least squares, describing the relationship between flipper length and body mass for these penguins. 

3 pieces:

- What type of model? 
- What is the relationship to model (dependent variable as a function of independent variable(s))? >> DV ~ IV
- Where is the data that is used to create this model?

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)

penguin_lm
```

### Brook package returns model outputs as tidy data frames

```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

penguin_lm_tidy

broom::glance(penguin_lm) # We will talk more about these on Wednesday, 11/3 (in two days)
```

How can I actually include my model equation in a report? 

```{r}
extract_eq(penguin_lm, use_coefs = TRUE)
```

```{r}
plot(penguin_lm)
```









